\TheTitle

### 2017-07-14 paper/conclusion.tex
more comments

@@

We implement a tool, \tool, using the \mt model, which allows a user to
filter the commits with a simple search interface. Once the user finds
the commit that they are interested in, they are provided simple
aggregated tables showing the files that were modified, the authors that
made the modifications, among other information. They are also provided
with three visualizations, a list tree, a pack tree, and a
Reingold-Tilford tree view. The list tree enables easy searching for
textual features, while the pack tree is good for visualizing the
structure of large \mt{s}, and the Reingold-Tilford tree is better
at visualizing the structure of small \mt{s}.

To ensure that our model is necessary, we evaluate the ability of users
to perform simple conceptual tasks, finding how a commit was merged into
the master branch of the Linux repository, and determining other commits
that were merged with the given merge. Finding that the participants in
our study were unable to perform this task, we compared the ability of
the participants to summarize key pieces of information aggregated in
these groups of commits. We asked for information about what files were
modified, the authors making the changes, among other tasks. Finally, we
asked the participants about their preference in tools, and which
aspects of each they preferred. We found that the participants in our
study were able to identify the correct answer more quickly and
accuractly using the \mt visualization than they were able to with
visualizations of the DAG.

Given that visualization of the model provides users with a better
understanding of events in the repository, we describe some issues with
identifying the master branch of the repository and a more generalized
approach to constructing \mt{s}. We implement the generalized approach
as a Bitbucket plugin to verify that it is able to quickly produce
results online, unlike in the implementation of \tool.

Participants in our study found them to be more enjoyable for
summarization tasks than visualizations of the DAG.\@ While there are
some issues with identifying the master branch in a robust manner, \mt
visualizations are an effective means of providing a clear conceptual
understanding and simple summarization of the events being merged into a
the master branch of a repository.

>>>>

\section{Conclusion}
\label{sec:conclusion}

\dmg{in this paper we describe, not develop}

@@

We implement a tool, \tool, using the \mt model, which allows a user to
filter the commits with a simple search interface. Once the user finds \dmg{user => they or he/she or users => they, tense issue?}
the commit that they are interested in, they are provided simple
aggregated tables showing the files that were modified, the authors that
made the modifications, among other information. \dmg{they is very ambiguous: are we talking authors, users, tables,
  files? be precise}
They are also provided
with three visualizations, a list tree, a pack tree, and a
Reingold-Tilford tree view. The list tree enables easy searching for
textual features, while the pack tree is good for visualizing the
structure of large \mt{s}, and the Reingold-Tilford tree is better
at visualizing the structure of small \mt{s}.

\dmg{not necessary: useful, and not only the model, but the implementation}
To ensure that our model is necessary, we evaluate the ability of users
to perform simple conceptual tasks \dmg{using linvis and comparing it with ... be precise}
, finding how a commit was merged into
the master branch of the Linux repository, and determining other commits
that were merged with the given merge. Finding that the participants in
our study were unable to perform this task \dmg{using gitk?, be precise, but you didn't ask them to compare based on
  their unability to perform the task, they were ask to do it nonetheless}, we compared the ability of
the participants to summarize key pieces of information aggregated in
these groups of commits. We asked for information about what files were
modified, the authors making the changes, among other tasks\dmg{among other tasks? tasks are T1...Tn. Don't overload
  uses of a word}. Finally, we
asked the participants about their preference in tools, and which
aspects of each they preferred. We found that the participants in our
study were able to identify the correct answer more quickly and
accuractly using the \mt visualization than they were able to with
visualizations of the DAG.

Given that visualization of the model provides users with a better
understanding of events in the repository, we describe some issues with
identifying the master branch of the repository and a more generalized
approach to constructing \mt{s}. We implement \dmg{this should be past tense} the generalized approach
as a Bitbucket plugin to verify that it is able to quickly produce
results online, unlike in the implementation of \tool.\dmg{the most important aspect is nto that it can quickly produce
  results, but that it can be applied to any repo in bitbucket}

Participants in our study found them \dmg{who/what is them?} to be more enjoyable for
summarization tasks than visualizations of the DAG.\@ While there are
some issues \dmg{with what tool? linvis?, \mt should be in the first phrase, not the ending phrase} with identifying the master branch in a robust manner, \mt
visualizations are an effective means of providing a clear conceptual
understanding and simple summarization of the events being merged into a
the master branch of a repository.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "lineval.tex"
%%% End:

### 2017-07-14 paper/discussion.tex
more comments

The results show conclusive results; the DAG visualization is unable to
adequately provide users with an explanation of the changes being made
in the repository, the DAG visualizatoin is not easily understood, and
is unable to provide summarizations of the changes being made at a
merge. Meanwhile, the \mt visualization is better able to provide an
explanation of how a commit is integrated, along with better
summarization. In this section, we discuss some observations, threats to
the validity, and comments made by the participants during the study
followed by discussion about modifications to the original algorithm to
help generalize it for more repositories, concluded with future work.

@@

During the course of the study, we noticed an issue that was consistent
among the participants when using Gitk; the most difficult challenge was
identifying the master branch of the repository. Many participants would
identify the tag as being the ``master branch'', but a tag is not a
branch. The visualization of the DAG does not provide any notion of
which branch being shown is the master branch. The default assumption is
that the first branch on the left is the master branch, but this is not
a good assumption. Furthermore, the visualization in Gitk is not
consistent, the ordering of the branches changes between runs, so
identifying the branch once will not guarantee that it will be
identifiable after restarting Gitk.

If users were able to easily identify the master branch using the
visualizations of the DAG, the results of the study would likely be very
different. This would certainly be the case for the single-commit tree;
it is trivial to summarize information about a single item, but
identifying that there was only a single commit in the tree was
non-trivial. This information is important because many trees contain a
single commit, and the structure of these trees is identical to the
structure of flat trees. Flat trees are the most common branching
structure in the repository, with the root being the parent to all of
the other nodes in the tree; to improve summarization and comprehension
of these trees, it would likely by sufficient to indicate the master
branch in the DAG visualization.

@@

One participant in the study worked as a release manager for more than
three years, working with both SVN and CVS repositories, but had little
experience with git. This subsection contains improvements made by this
participant during the study and afterward.

Contributors making merges need to understand more than just what merges
a commit was collected into before reaching the repository of the
contributor. It is also important to understand order that the related
commits were made, as the order tells the story of what the developer
was thinking as they were writing the changes. The current \mt model
does not order the commits, simply placing them randomly. This is the
primary reason behind this participant's request to use both
simultaneously. \tool is able to help with the aggregation of the
information, and provide a better understanding of the next merge
involved in integrating this commit, but the DAG visualization in Gitk
provides the full story of the commit instead of hiding it behind a
layer of abstraction.

@@

The answers provided by the participants to earlier tasks were not
taken into account for determining the accuracy. If the participant was
unable to determine the correct commits for the tree within the
conceptual task group, the summarization results would be recorded as
wrong, even if the summarization they provided was correct for the set
of commits selected to be part of the tree. A further study could be
done where the correct answer was provided to the participant after each
task so that errors would not propagate between tasks.

@@

We were only able to work with 12 participants. We apply various
statistical tests to ensure that our findings are reasonable.

@@

% A possible
% reason for this may be that unless a repository reaches a sufficient
% complexity, both in branching and number of commits, these tools are
% unnecessary for the normal operation of git. Furthermore, fear of the
% complexity caused by branching may cause personal and academic
% repositories to have relatively simple structures. While they were
% unfamiliar with the DAG structure, these users were also unfamiliar with
% the \mt model, and were still able to better understand and summarize
% the repository using \tool.

@@

If this algorithm is to be generalized into a dynamic, web-based, tool,
it may not be feasible to download every every repository event in the
repository in a reasonable period of time. We instead look toward a
breadth-first approach at limiting the number of repository events that
must be downloaded.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "userstudy"
%%% End:

>>>>

\section{Discussion}
\label{sec:discussion}

The results show conclusive results; the DAG visualization \dmg{provided by gitk...} is unable to \dmg{this is a very
  long sentence that does not read very well}
adequately provide users with an explanation of the changes being made
in the repository, the DAG visualization is not easily understood, and
is unable to provide summarizations of the changes being made at a
merge. Meanwhile, the \mt visualization \dmg{of linvis...} is better able to provide an
explanation of how a commit is integrated, along with better
summarization. In this section, we discuss some observations, threats to
the validity, and comments made by the participants during the study
followed by discussion about modifications to the original algorithm to
help generalize it for more repositories, concluded with future work.

@@

During the course of the study, we noticed an issue that was consistent
among the participants when using Gitk; \dmg{wrong use of semicolon} the most difficult challenge was
identifying the master branch of the repository. Many participants would
identify the tag as being the ``master branch'', but a tag is not a
branch (it simply points to a given commit). The visualization of the DAG does not provide any notion of
which branch being shown is the master branch. The default assumption is
that the first branch on the left is the master branch, but this is not
always correct. Furthermore, the visualization in Gitk is not
consistent, the ordering of the branches changes between runs, so
identifying the branch once will not guarantee that it will be
identifiable after restarting Gitk.\dmg{i didn't know the ordering is non-deterministic, are you sure? make sure you are
sure, sure? :)}

If users were able to easily identify the master branch using the
visualizations of the DAG, the results of the study would likely be very
different\dmg{be explicit eg.: that there was very little difference, if any, between the use of both tools}. This would
certainly be the case for the single-commit tree; \dmg{another wrong use, i want you to read the description of colon vs
semicolon and scan the paper for them to make sure they are used correctly}
it is trivial to summarize information about a single item, but
identifying that there was only a single commit in the tree was
non-trivial. This information is important because many trees contain a
single commit, and the structure of these trees is identical to the
structure of flat trees. Flat trees are the most common branching
structure in the repository, with the root being the parent to all of
the other nodes in the tree; to improve summarization and comprehension
of these trees, it would likely by sufficient to indicate the master
branch in the DAG visualization.

@@

One participant in the study worked as a release manager for more than
three years, working with both SVN and CVS repositories, but had little
experience with git. This subsection contains improvements made by this
participant during the study and afterward.\dmg{he made improvements? to what? Isn't this section about his views of
  what is needed?}

Contributors making merges need to understand more than just what merges
a commit was collected into before reaching the repository of the
contributor. It is also important to understand order that the related
commits were made, as the order tells the story of what the developer
was thinking as they were writing the changes. The current \mt model
does not order the commits, simply placing them randomly. \dmg{this surprised me. we order the commits in the tree, you
  know which is before which, so this is more an issue of you not displaying the data than we not having it} This is the
primary reason behind this participant's request to use both \dmg{tools}
simultaneously. \tool is able to help with the aggregation of the
information, and provide a better understanding of the next merge
involved in integrating this commit, but the DAG visualization in Gitk
provides the full story of the commit instead of hiding it behind a
layer of abstraction.

@@

The answers provided by the participants to earlier tasks were not
taken into account for determining the accuracy\dmg{accuracy of what? the stattement is not clear to me. Oh, i think you
mean, if they get an answer wrong it might impact the results of some following tasks; you can be more precise in the description}. If the participant was
unable to determine the correct commits for the tree within the
conceptual task group, the summarization results would be recorded as
wrong, even if the summarization they provided was correct for the set
of commits selected to be part of the tree. A further study could be
done where the correct answer was provided to the participant after each
task so that errors would not propagate between tasks.

@@

We were only able to work with 12 participants. We apply various
statistical tests to ensure that our findings are statistically significant.

@@

\dmg{add a couple of sentences on the fact that these were students, some with industrial experience. People who are
  professinals might do better}

% A possible

% reason for this may be that unless a repository reaches a sufficient
% complexity, both in branching and number of commits, these tools are
% unnecessary for the normal operation of git. Furthermore, fear of the
% complexity caused by branching may cause personal and academic
% repositories to have relatively simple structures. While they were
% unfamiliar with the DAG structure, these users were also unfamiliar with
% the \mt model, and were still able to better understand and summarize
% the repository using \tool.

\dmg{the following should be a section on its own, because it is no longer part of the study, also
use a better title: generalization of the creation of the merge-tree?}

@@

\dmg{you don't generalize an alg into a tool; you implement the algorithm in a tool}
If this algorithm is to be generalized into a dynamic, web-based, tool,
it may not be feasible to download every every repository event in the
repository in a reasonable period of time. We instead look toward a
breadth-first approach at limiting the number of repository events that
must be downloaded.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "lineval.tex"
%%% End:

### 2017-07-14 paper/study.tex
more comments

\begin{table}[htpb]
  \centering
  \caption{Cross-Commit Results\evan{Should I group the results by task
      or by metric? It's by metric right now}}
  \label{tab:cross_commit_results}
  \begin{tabular}{ccrl}
    \toprule
    Task & Metric      & $p$-value & Conclusion\\\midrule
    T4   & Correctness & 0.22      & Do not reject $H_0$\\
    T5   & Correctness & 0.04      & Reject $H_0$\\
    T6   & Correctness & 0.13      & Do not reject $H_0$\\
    T7   & Correctness & 0.06      & Do not reject $H_0$\\
    T8   & Correctness & 0.07      & Do not reject $H_0$\\
    T9   & Correctness & 0.04      & Reject $H_0$\\
    T10  & Correctness & 0.62      & Do not reject $H_0$\\

@@

  \begin{tabular}{ m{6cm} m{6cm} }
    \includegraphics[width=6cm]{figures/userstudy/correctness/5.pdf} &
    \includegraphics[width=6cm]{figures/userstudy/correctness/9.pdf}
  \end{tabular}
  \caption{Unaggregated Correctness results for T5 and T9 \evan{Split
      this? Is it clear that between Commit 2 and Commit 1 is where the
    separation of the plots is?}}
  \label{fig:correctness_t5_t9}
\end{figure*}

@@

@@

@@

Among the 12 participants, there was nearly unanimous agreement that for
conceptual understanding and summarization tasks; \tool was easier to
work with than Gitk. The participants cited the ability to abstract
information about the merge from the clean summarization tables and
simple visualizations. Three participants suggested that someone with a
professional understanding of Gitk and the git command-line may be to
extract a conceptual understanding from the DAG visualization and
perform the summarization tasks. One of these three participants said
that they would prefer to have both tools available, as they are able to
complement each other.

>>>>

\begin{table}[htpb]
  \centering
  \caption{Cross-Commit Results\dmg{Be more descriptive in the captions.People read the papers via tables and
      pictures. What does the table say? e.g. as it can be seen.... tell a story with the picture, instead of asking the
    reader to make up the story... which might be different than the one you want them to have}}
  \label{tab:cross_commit_results}
  \begin{tabular}{ccrl}
    \toprule
    Task & Metric      & $p$-value & Conclusion\\\midrule
    T4   & Correctness & 0.22      & Do not reject $H_0$\\
    T5   & Correctness & 0.04      & Reject $H_0$\\
    T6   & Correctness & 0.13      & Do not reject $H_0$\\
    T7   & Correctness & 0.06      & Do not reject $H_0$\\
    T8   & Correctness & 0.07      & Do not reject $H_0$\\
    T9   & Correctness & 0.04      & Reject $H_0$\\
    T10  & Correctness & 0.62      & Do not reject $H_0$\\

@@

  \begin{tabular}{ m{6cm} m{6cm} }
    \includegraphics[width=6cm]{figures/userstudy/correctness/5.pdf} &
    \includegraphics[width=6cm]{figures/userstudy/correctness/9.pdf}
  \end{tabular}
  \caption{Unaggregated Correctness results for T5 and T9.}
  \label{fig:correctness_t5_t9}
\end{figure*}

@@

\dmg{you wrongly use ``semicolon'', you mean ``colon''. Same below...}

@@

\dmg{Emphasize: To summarize...}

@@

Among the 12 participants, there was nearly unanimous agreement that for
conceptual understanding and summarization tasks; \dmg{this is another wrong use of semicolon}\tool was easier to
work with \dmg{avoid idiomatic expressions: what does ``work with'' mean? use a precise verb. English is a rich language.} than Gitk. The participants cited the ability to abstract
information about the merge from the clean summarization tables and
simple visualizations \dmg{be precise: from Linvis' clean summarization tables and ... }. Three participants suggested that someone with a
professional understanding of Gitk and the git command-line may be able to
extract a conceptual understanding from the DAG visualization and
perform the summarization tasks. One of these three participants said
that they would prefer to have both tools available, as they are able to
complement each other.
